|

### 2023-03-16 paper/01-introduction.Rmd
simplified sub-files; removed headers
Small updates.  Added some citations.

---
bibliography: bibliography.bib
output: rticles::asa_article
---

@@

@Burke2018Created

>>>>

@@

@Burke2018Created
@AlamarGoldner2013: They talk about how there is no data available to measure offensive line performance.  1259 plays, 20 teams, 2010 season.  Success of each offensive lineman was evaluated using the best judgement of the observer.   Collected time in pocket.  They collected a bunch of binary variables and did this all by HAND!  Estimate a survival model for each position on the offensive line.  They don't rank individuals, but rather positions on a team.  They then use the predicted probability as a covariate in a model to predict completion.

@AlamarGould2008
